### 2019-07-26 paper/paper.tex
Update paper.tex

%%%%%%%%%%%%%%%%%% Table 3
\begin{table}[htbp]
  \centering
\tbl{Execution times for different OLS algorithms in R, Stata and Julia}{
    \begin{tabular}{|c|c|c|c|c|}
    \hline
      & GlobalSearchRegression.jl &R-lm & Stata-reg & GLM.jl \\
    \hline
    Execution time & 0.012 & 0.06 & 0.2 & 0.023 \\
    \hline
    Speed-up & 1 & 5 & 16.67 & 1.92 \\
    \hline
    \end{tabular}}
    \begin{tablenote}
    Note: Execution times were obtained using a i7-7500 dual-core build, with 8 GiB of DDR4 RAM, under Windows 10 and running Julia 1.1.0, Stata 13 and RStudio 3.6.0. Speed-ups are obtaining dividing each execution time by the GlobalSearchRegression.jl execution time.
    \end{tabnote}
\end{table}

>>>>

%%%%%%%%%%%%%%%%%% Table 3
\begin{table}[h]
  \centering
\tbl{Execution times for different OLS algorithms in R, Stata and Julia}{
    \begin{tabular}{|c|c|c|c|c|}
    \hline
      & GlobalSearchRegression.jl & R-lm & Stata-reg & GLM.jl \\
    \hline
    Execution time & 0.012 & 0.06 & 0.2 & 0.023 \\
    \hline
    Speed-up & 1 & 5 & 16.67 & 1.92 \\
    \hline
    \end{tabular}}
    \begin{tabnote}
    Note: Execution times were obtained using a i7-7500 dual-core build, with 8 GiB of DDR4 RAM, under Windows 10 and running Julia 1.1.0, Stata 13 and RStudio 3.6.0. Speed-ups are obtaining dividing each execution time by the GlobalSearchRegression.jl execution time.
    \end{tabnote}
\end{table}
